Internal models of type theory

### 2013-11-10 article-models-tt.tex
added remark on stability under extension

>>>>

\subsection{Stability under extension}
We need to come up with a suitable notion of stability under extension, which
is to be the type theoretical analogue of category theoretical stability under
slicing. When we have done this, we have to show that the constructions we have
so far are indeed stable under extension.
